---
title: "0-PPT"
author: "Fabio CRUZ"
date: "9/13/2020"
output: revealjs::revealjs_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Presentation



## Test

```{r}
knitr::include_url("https://lf2l.github.io/reproducible-research/PPT/#/")
```



## Test
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

--- 
## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

---

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

---

## Slide with Plot

```{r pressure}
plot(pressure)
```


## Slide 

```{r, figures-side, fig.show="hold", out.width="50%"}
par(mar = c(4, 4, .1, .1))
plot(cars)
plot(mpg ~ hp, data = mtcars, pch = 19)
```



